---
title: "week 3 developing data"
author: "Nikhitha
date: "/11/2020"
output: html_document
---

```{r}
library(plotly)
data(m_c)
head(m_c)
```
```{r}
plot_ly(m_c) %>%
    add_trace(x = ~mpg, y = ~cyl, type="scatter", mode = "markers",name = "cylinder", legendgroup = "cylinder", 
              marker = list(color = "#52A9BD")) %>%
    add_trace(x = ~mpg, y = ~gear, type="scatter", mode = "markers",
              name = "gear", legendgroup = "gear", 
              marker = list(color = "#FFF16B")) %>%
    add_trace(x = ~mpg, y = ~carb, type="scatter", mode = "markers",
              name = "carb", legendgroup = "carb", 
              marker = list(color = "#F5677D")) 
```
absgyusd vysdgvfushv  bjhugvkdjvh bdfkuvh,ksdmj byfugvfhvn vyugvdrjgv vujsvgjrhbvd asujcjfbhvjac bivucjc dbcvaujhjrkcnm dbgvsdfjvm
vbruiqvjn bfvjmrvntrkjgmtgniotkgmtr bntgikbjtnbyitkhjm btuiwgjktgntiobktjbhtoigjkmw thiknyhbrynhiokryjmhfdjynkjgfbwnjkm
bcuh busgjh bvaujfmn bavujvmbd r av8usjchuj fgwfuejfuhnwem vuvjhtrnwmvujesgj, busvjam vvbisdkvnz  sbjkmzn bwviskuzjn vgujnefjsvk, nejkghwetnigj gqwerhign tgvrtjgtwiugtjnm vuiewrgnqkm gbujhrng qbujbrfvh vjgmsergktle;l;oifhwuifoe-rqof9345ty8u23i9 qfbg ujh olg\r
qkgjhrufiopgtogheroeegrwalajhsfluisrfy xhnluifghrjmjvnruifn vhruiajenm rrmiejeuijml
